# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r,echo=TRUE}
dt<-read.csv(unz('activity.zip','activity.csv'))
```
Add a new variable in the dataset: 
* newID: an identifier for the 5-minute interval within the day (a progressive integer  from 1 to 288).

```{r,echo=TRUE}
newID<-vector(mode="numeric",length=dim(dt)[1])

for(i in 1:dim(dt)[1]){
	newID[i]=ifelse(i%%288==0, 288, i%%288);
}
dt$newID<-newID
```

## What is mean total number of steps taken per day?
```{r,echo=TRUE}
TotSteps<-tapply(dt$steps,as.factor(dt$date),sum,na.rm=TRUE)
hist(as.vector(TotSteps),breaks=10,main='Total number of steps taken per day',xlab='Number of steps',ylab='',col='blue')
```

Mean and Median of total number of steps taken per day
```{r,echo=TRUE}
s<-summary(TotSteps)
print(paste("Median =",s["Median"]))
print(paste("Mean =",s["Mean"]))
```


## What is the average daily activity pattern?
```{r}
IntvAvg<-tapply(dt$steps,as.factor(dt$interval),mean,na.rm=TRUE)
```

Time series plot of the 5-minute interval and the average number of steps taken, averaged across all days

```{r}
plot(as.numeric(unique(dt$interval)),IntvAvg,type='l',main='Average number of steps taken per 5- minute interval',xlab='5- minute interval',ylab='Number of steps',col='red')
```

5- minute interval with the maximum number of  steps on average
```{r}
print(paste("5-minute interval id: ",names(which.max(IntvAvg))));
```

```{r}
print(paste("maximum number of  steps on average: ",IntvAvg[which.max(IntvAvg)]))
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
