# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r,echo=TRUE}
dt<-read.csv(unz('activity.zip','activity.csv'))
```
Add a new variable in the dataset: 


Add a new factor variable with two levels – “weekday” and “weekend” indicating whether a given date is weekend (Saturday or Sunday) or a weekday 
day

```{r}
temp<-vector(mode="character",length=dim(dt2)[1])
for(i in 1:dim(dt)[1]){
	a<-strptime(dt$date[i],"%Y-%m-%d")
	temp[i]=ifelse((a$wday==0) | (a$wday==6),"weekend","weekday");
}
dt$wd=as.factor(temp)
```


## What is mean total number of steps taken per day?
```{r,echo=TRUE}
TotSteps<-tapply(dt$steps,as.factor(dt$date),sum,na.rm=TRUE)
hist(as.vector(TotSteps),breaks=10,main='Total number of steps taken per day',xlab='Number of steps',ylab='',col='blue')
```

Mean and Median of total number of steps taken per day
```{r,echo=TRUE}
s<-summary(TotSteps)
print(paste("Median =",s["Median"]))
print(paste("Mean =",s["Mean"]))
```


## What is the average daily activity pattern?
```{r,echo=TRUE}
IntvAvg<-tapply(dt$steps,as.factor(dt$interval),mean,na.rm=TRUE)
```

Time series plot of the 5-minute interval and the average number of steps taken, averaged across all days

```{r,echo=TRUE}
plot(as.numeric(unique(dt$interval)),IntvAvg,type='l',main='Average number of steps taken per 5- minute interval',xlab='5- minute interval',ylab='Number of steps',col='red')
```

5- minute interval with the maximum number of  steps on average
```{r,echo=TRUE}
print(paste("5-minute interval id: ",names(which.max(IntvAvg))));
```

```{r,echo=TRUE}
print(paste("maximum number of  steps on average: ",IntvAvg[which.max(IntvAvg)]))
```

## Imputing missing values

Total number of missing values in the dataset

```{r,echo=TRUE}
print(paste("Number of missing value: ",nrow(dt[is.na(dt$steps)==T | is.na(dt$date)==T | is.na(dt$interval),])))
```

dt2 is a new dataset equal to the original dataset but with the missing data replaced with the mean for that 5-minute interval
```{r,echo=TRUE}
dt2<-dt;

newsteps<-vector(nrow(dt),mode="numeric")
for(i in 1:nrow(dt)){
	newsteps[i]=ifelse(is.na(dt$steps[i])==T,IntvAvg[as.character(dt$interval[i])],dt$steps[i]);
}

dt2$steps<-newsteps;
```

Total number of steps taken each day according the new dataset

```{r,echo=TRUE}
TotSteps2<-tapply(dt2$steps,as.factor(dt2$date),sum,na.rm=TRUE)
hist(as.vector(TotSteps2),breaks=10,main='',xlab='Number of steps',ylab='',col='blue')
```

Mean and median of the new dataset

```{r,echo=TRUE}
s2<-summary(TotSteps2)
print(paste("Median =",s2["Median"]))
print(paste("Mean =",s2["Mean"]))
```

Differences between the new dataset and the original one
```{r,echo=TRUE}
print(paste("Differences between the two Median =",s2["Median"] - s["Median"]))
print(paste("Differences between the two Mean =",s2["Mean"]- s["Mean"]))
```

## Are there differences in activity patterns between weekdays and weekends?

Differences in activity patterns between weekdays and weekends
```{r}
dt2_we=dt2[dt2$wd=="weekend",]
dt2_wd=dt2[dt2$wd=="weekday",]

IntvAvg_we<-tapply(dt2_we$steps,as.factor(dt2_we$interval),mean)
IntvAvg_wd<-tapply(dt2_wd$steps,as.factor(dt2_wd$interval),mean)


par(mfrow=c(2,1))
plot(as.numeric(names(IntvAvg_we)),IntvAvg_we,type='l',main='weekend',xlab='5- minute interval',ylab='Number of steps',col='blue')
plot(as.numeric(names(IntvAvg_wd)),IntvAvg_wd,type='l',main='weekday',xlab='5- minute interval',ylab='Number of steps',col='blue')

```